Modelling state-switching functional data with hidden Markov models: supplementary material (simulation study)

### 2021-06-21 Report/Supp_Sim.tex
Updates from Overleaf

    	\noindent Figure \arabic{fignum}: Acceleration data for a five dives of a selected simulated data set. The raw accelerometer data is denoted as $Y^*_{t,\tilde t^*}$ and recorded at 50 times per second while $\Zone_{t,\tilde t^*}$ and $\Ztwo_{t,\tilde t^*}$ are recorded at once every two seconds. Dives are separated by vertical black lines. The colour of the curve corresponds to the true fine-scale state, while the colour of the background corresponds to the true dive type. Subdive state 1 can plausibly be interpreted as ``gliding", subdive state 2 can plausibly be interpreted as active swimming, and subdive state 3 can be interpretted as sudden or aggressive movement.
    	\addtocounter{fignum}{1}

@@

        \noindent Table \arabic{tablenum}: Average decoding accuracies and training times for all models used to categorize dive type and subdive state in the simulation study. Each of the four models was fit to 500 training data sets comprised of 100 simulated dives and tested on test data sets also comprised of 100 simulated dives. Reported values are averages, and $\pm$ refers to the sample standard deviation across the 500 data sets. Rows labelled Both/Both correspond to overall average decoding accuracy.
        \addtocounter{tablenum}{1}

@@

\multirow{4}{*}{CarHHMM-DFT}& \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.337$                         & $0.067$ $(p=0.287)$          & $1.393$                             & $1.025 \pm 0.124$                             \\
                            &                               & 2                             & $127.140$                         & $0.070$ $(p=0.945)$          & $22.562$                             & $15.710 \pm 6.726$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.801$                         & $-0.109$ $(p=0.035)$          & $1.154$                             & $0.838 \pm 0.110$                             \\
                            &                               & 2                             & $59.520$                         & $-4.540$ $(p=0.000)$          & $17.678$                             & $13.040 \pm 5.530$                             \\ \hline
\multirow{4}{*}{HHMM-DFT}   & \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.373$                         & $0.103$ $(p=0.084)$          & $1.327$                             & $1.030 \pm 0.113$                             \\
                            &                               & 2                             & $126.843$                         & $-0.227$ $(p=0.818)$          & $22.004$                             & $15.367 \pm 6.105$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.860$                         & $-0.050$ $(p=0.351)$          & $1.187$                             & $0.845 \pm 0.110$                             \\
                            &                               & 2                             & $57.136$                         & $-6.924$ $(p=0.000)$          & $16.118$                             & $12.624 \pm 5.165$                             \\ \hline
\multirow{4}{*}{CarHHMM}    & \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.248$                         & $-0.022$ $(p=0.826)$          & $2.196$                             & $1.042 \pm 0.138$                             \\
                            &                               & 2                             & $117.624$                         & $-9.446$ $(p=0.000)$          & $34.336$                             & $15.251 \pm 7.111$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.523$                         & $-0.387$ $(p=0.001)$          & $2.594$                             & $0.858 \pm 0.148$                             \\
                            &                               & 2                             & $56.981$                         & $-7.079$ $(p=0.000)$          & $16.325$                             & $12.530 \pm 6.095$                             \\ \hline
\multirow{4}{*}{CarHMM-DFT} & \multirow{2}{*}{$\mu_Y$}      & 1                             & $41.685$                         & ---                        & $4.268$                             & $2.001 \pm 0.347$                             \\

@@

                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $30.299$                         & ---                        & $5.439$                             & $1.948 \pm 0.443$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimates of the distributions of estimates of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the HHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

\multirow{9}{*}{CarHHMM}    & \multirow{3}{*}{$\mu_A^*$}    & 1                                & $0.060$                         & $0.060$ $(p=0.000)$          & $0.034$                             & $0.024 \pm 0.054$                             \\
                            &                               & 2                                & $0.097$                         & $-0.003$ $(p=0.000)$          & $0.016$                             & $0.052 \pm 0.055$                             \\
                            &                               & 3                                & $0.201$                         & $0.001$ $(p=0.634)$          & $0.058$                             & $0.018 \pm 0.007$                             \\
                            & \multirow{3}{*}{$\sigma_A^*$} & 1                                & $0.111$                         & $0.061$ $(p=0.000)$          & $0.004$                             & $0.006 \pm 0.042$                             \\
                            &                               & 2                                & $0.285$                         & $0.185$ $(p=0.000)$          & $0.009$                             & $0.040 \pm 0.043$                             \\ 
                            &                               & 3                                & $1.150$                         & $0.850$ $(p=0.000)$          & $0.080$                             & $0.003 \pm 0.001$                             \\
                            & \multirow{3}{*}{$\phi_A^*$}   & 1                                & $0.830$                         & $-0.140$ $(p=0.000)$          & $0.048$                             & $0.016  $                             \\
                            &                               & 2                                & $0.004$                         & $-0.826$ $(p=0.000)$          & $0.012$                             & $0.023  $                             \\
                            &                               & 3                                & $0.000$                         & $-0.610$ $(p=0.000)$          & $0.000$                             & $0.016 \pm 0.004$                             \\ \hline

@@

        \noindent Table \arabic{tablenum}: Estimates and standard errors for the parameters of the distribution of acceleration across all four models in the simulation study. The ``Estimate" column is the average across 500 simulations, and the ``Observed Fisher SE" column is the median across 500 simulations. The $\pm$ refers to the inter-quartile range. SE stands for standard error. Reported $p$-values test if the observed bias is statistically significant using a one-sample $t$-test.
        \addtocounter{tablenum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of acceleration parameters ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of acceleration parameters ($\hat \mu^*_A$ and $\hat \sigma^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$ and $\sigma^*_A$ for both subdive states. These estimates are for the HHMM-DFT. Note that the HHMM-DFT assumes no auto-correlation in $\Zone_{t,\tilde t^*}$, so $\hat \phi_A^{*(\cdot,i^*)}$ is absent from these plots.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of acceleration parameters ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM. 
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of acceleration parameters ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

                            &                               & 3                                & $9787.1$                         & $17.2$ $(p=0.718)$           & $1060.5$                            & $280.2 \pm 97.1$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.849$                         & $-0.001$ $(p=0.991)$         & $0.989$                             & $0.652 \pm 0.094$                             \\
                            &                               & 2                                & $514.21$                         & $-2.47$ $(p=0.010)$          & $21.43$                             & $11.41 \pm 0.95$                             \\
                            &                               & 3                                & $14430$                          & $-33$ $(p=0.647)$            & $1596$                              & $303 \pm 166$                             \\ \hline

@@

                            &                               & 3                                & $6841.0$                         & $-2929.0$ $(p=0.000)$        & $1164.3$                            & $198.2 \pm 74.7$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.800$                         & $-0.050$ $(p=0.351)$         & $1.192$                             & $0.676 \pm 0.104$                             \\
                            &                               & 2                                & $513.26$                         & $-3.42$ $(p=0.001)$          & $22.60$                             & $12.50 \pm 1.30$                             \\
                            &                               & 3                                & $11459$                          & $-3004$ $(p=0.000)$          & $1739$                              & $303 \pm 194$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.890$                         & $0.040$ $(p=0.401)$          & $1.058$                             & $0.656 \pm 0.101$                             \\
                            &                               & 2                                & $515.23$                         & $-1.45$ $(p=0.125)$          & $21.09$                             & $11.37 \pm 0.99$                             \\
                            &                               & 3                                & $14437$                          & $-25$ $(p=0.740)$          & $1661$                             & $332 \pm 166$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of wiggliness parameters ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of wiggliness parameters ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the HHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of estimates of wiggliness parameters ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \begin{center}
        \scalebox{0.75}{
        \bgroup
        \centering
        \def\arraystretch{1.5}
\begin{tabular}{ccccccc}
Model                        & \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Estimate}   & \multicolumn{1}{c}{Bias} & \multicolumn{1}{c}{Empirical SE} & \multicolumn{1}{c}{Observed Fischer SE}     \\ \hline
\multirow{2}{*}{CarHHMM-DFT}& $\Gamma_{12}$                 & $0.160$                         & $0.005$ $(p=0.030)$        & $0.056$                           & $0.042 \pm 0.012$                             \\
                             & $\Gamma_{21}$                 & $0.907$                         & $-0.006$ $(p=0.214)$        & $0.102$                           & $0.116$                             \\ \hline
\multirow{2}{*}{HHMM-DFT}   & $\Gamma_{12}$                 & $0.161$                         & $0.007$ $(p=0.007)$        & $0.055$                           & $0.041 \pm 0.011$                             \\
                             & $\Gamma_{21}$                 & $0.916$                         & $0.004$ $(p=0.372)$        & $0.088$                           & $0.112$                             \\ \hline
\multirow{2}{*}{CarHHMM}    & $\Gamma_{12}$                 & $0.198$                         & $0.044$ $(p=0.000)$        & $0.152$                           & $0.044 \pm 0.014$                             \\
                             & $\Gamma_{21}$                 & $0.832$                         & $-0.081$ $(p=0.000)$        & $0.195$                           & $0.103 \pm 0.073$                             \\ \hline
\multirow{2}{*}{CarHMM-DFT} & $\Gamma_{12}$                 & ------                         & ------                   & ------                           & ------                                      \\
                             & $\Gamma_{21}$                 & ------                         & ------                   & ------                           & ------                                      \\
\end{tabular}
        \egroup
        }
        \end{center}

        \noindent Table \arabic{tablenum}: Estimates and standard errors for coarse-scale probability transition matrices across all four models in the simulation study. The ``Estimate" column is the average across 500 simulations, and the ``Observed Fisher SE" column is the median across 500 simulations. The $\pm$ refers to the inter-quartile range. SE stands for standard error. Reported $p$-values test if the observed bias is statistically significant using a one-sample $t$-test.
        \addtocounter{tablenum}{1}

@@

                             & $\Gamma^{*(1)}_{13}$          & $0.002$                         & $0.002$ $(p=0.000)$        & $0.004$                           & $\text{N/A}$                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.003$                         & $0.003$ $(p=0.000)$        & $0.008$                           & $\text{N/A}$                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.111$                         & $0.146$ $(p=0.349)$        & $0.017$                           & $0.015 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.001$                         & $0.002$ $(p=0.000)$        & $0.002$                           & $\text{N/A}$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.151$                         & $-0.068$ $(p=0.584)$        & $0.023$                           & $0.021 \pm 0.005$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.036$                         & $0.016$ $(p=0.944)$        & $0.013$                           & $0.010 \pm 0.003$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.007$                         & $0.003$ $(p=0.000)$        & $0.024$                           & $\text{N/A}$                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.252$                         & $0.008$ $(p=0.000)$        & $0.096$                           & $0.063 \pm 0.028$                             \\ \hline

@@

                             & $\Gamma^{*(1)}_{13}$          & $0.003$                         & $0.003$ $(p=0.000)$        & $0.006$                           & $\text{N/A}$                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.005$                         & $0.005$ $(p=0.000)$        & $0.009$                           & $\text{N/A}$                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.109$                         & $0.128$ $(p=0.000)$        & $0.018$                           & $0.016 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.002$                         & $0.003$ $(p=0.000)$        & $0.004$                           & $\text{N/A}$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.151$                         & $-0.073$ $(p=0.712)$        & $0.031$                           & $0.023 \pm 0.006$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.037$                         & $0.012$ $(p=0.009)$        & $0.013$                           & $0.011 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.021$                         & $0.005$ $(p=0.000)$        & $0.026$                           & $0.034  $                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.135$                         & $-0.073$ $(p=0.000)$        & $0.057$                           & $0.038 \pm 0.018$                             \\ \hline
\multirow{12}{*}{CarHHMM}    & $\Gamma^{*(1)}_{12}$          & $0.138$                         & $-0.114$ $(p=0.000)$        & $0.131$                           & $0.018 \pm 0.006$                             \\
                             & $\Gamma^{*(1)}_{13}$          & $0.023$                         & $0.022$ $(p=0.000)$        & $0.107$                           & $0.039  $                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.013$                         & $0.013$ $(p=0.000)$        & $0.022$                           & $0.013  $                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.056$                         & $0.026$ $(p=0.000)$        & $0.035$                           & $0.008 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.002$                         & $0.022$ $(p=0.004)$        & $0.017$                           & $\text{N/A}$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.069$                         & $-0.113$ $(p=0.000)$        & $0.032$                           & $0.011 \pm 0.003$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.017$                         & $-0.009$ $(p=0.000)$        & $0.012$                           & $0.005 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.011$                         & $0.013$ $(p=0.000)$        & $0.016$                           & $0.029  $                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.138$                         & $-0.093$ $(p=0.000)$        & $0.079$                           & $0.037 \pm 0.018$                             \\ \hline

>>>>

    	\noindent Figure \arabic{fignum}: Acceleration data for a five dives of a selected simulated data set. The raw accelerometer data is denoted as $Y^*_{t,\tilde t^*}$ and recorded at 50 times per second while $\Zone_{t,\tilde t^*}$ and $\Ztwo_{t,\tilde t^*}$ are recorded at once every two seconds. Dives are separated by vertical black lines. The colour of the curve corresponds to the true subdive state, while the colour of the background corresponds to the true dive type. Subdive state 1 can plausibly be interpreted as ``gliding", subdive state 2 can plausibly be interpreted as active swimming, and subdive state 3 can be interpretted as sudden or aggressive movement.
    	\addtocounter{fignum}{1}

@@

        \noindent Table \arabic{tablenum}: Average decoding accuracies and training times for all models used to categorize dive type and subdive state in the simulation study. Each of the four models was fit to 500 training data sets comprised of 100 simulated dives and tested on test data sets also comprised of 100 simulated dives. Reported values are averages, and $\pm$ refers to the sample standard deviation across the 500 data sets. Rows labelled All/All correspond to overall average decoding accuracy.
        \addtocounter{tablenum}{1}

@@

\multirow{4}{*}{CarHHMM-DFT}& \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.33$                         & $0.07$ $(p=0.287)$          & $1.39$                             & $1.03 \pm 0.12$                             \\
                            &                               & 2                             & $127.14$                        & $0.07$ $(p=0.945)$          & $22.56$                             & $15.71 \pm 6.726$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.80$                         & $-0.11$ $(p=0.035)$          & $1.15$                             & $0.84 \pm 0.11$                             \\
                            &                               & 2                             & $59.52$                         & $-4.54$ $(p=0.000)$          & $17.68$                             & $13.04 \pm 5.53$                             \\ \hline
\multirow{4}{*}{HHMM-DFT}   & \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.37$                         & $0.10$ $(p=0.084)$          & $1.33$                             & $1.03 \pm 0.11$                             \\
                            &                               & 2                             & $126.84$                         & $-0.23$ $(p=0.818)$          & $22.00$                             & $15.37 \pm 6.11$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.86$                         & $-0.05$ $(p=0.351)$          & $1.19$                             & $0.85 \pm 0.11$                             \\
                            &                               & 2                             & $57.14$                         & $-6.92$ $(p=0.000)$          & $16.12$                             & $12.62 \pm 5.17$                             \\ \hline
\multirow{4}{*}{CarHHMM}    & \multirow{2}{*}{$\mu_Y$}      & 1                             & $27.25$                         & $-0.02$ $(p=0.826)$          & $2.20$                             & $1.04 \pm 0.14$                             \\
                            &                               & 2                             & $117.62$                         & $-9.45$ $(p=0.000)$          & $34.34$                             & $15.13 \pm 7.10$                             \\
                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $10.52$                         & $-0.39$ $(p=0.001)$          & $2.59$                             & $0.86 \pm 0.15$                             \\
                            &                               & 2                             & $56.98$                         & $-7.08$ $(p=0.000)$          & $16.33$                             & $12.53 \pm 5.95$                             \\ \hline
\multirow{4}{*}{CarHMM-DFT} & \multirow{2}{*}{$\mu_Y$}      & 1                             & $41.69$                         & ---                        & $4.27$                             & $2.00 \pm 0.35$                             \\

@@

                            & \multirow{2}{*}{$\sigma_Y$}   & 1                             & $30.30$                         & ---                        & $5.44$                             & $1.95 \pm 0.44$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the CarHHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of dive duration parameter estimates ($\hat \mu_Y$ and $\hat \sigma_Y$). These estimates are associated with the HHMM-DFT and correspond to both dive types. The red star represents the true values of $\mu_Y$ and $\sigma_Y$ for both dive types.
        \addtocounter{fignum}{1}

@@

\multirow{9}{*}{CarHHMM}    & \multirow{3}{*}{$\mu_A^*$}    & 1                                & $0.060$                         & $0.060$ $(p=0.000)$          & $0.034$                             & $0.019 \pm 0.006$                             \\
                            &                               & 2                                & $0.097$                         & $-0.003$ $(p=0.000)$          & $0.016$                             & $0.007 \pm 0.001$                             \\
                            &                               & 3                                & $0.201$                         & $0.001$ $(p=0.634)$          & $0.058$                             & $0.062 \pm 0.011$                             \\
                            & \multirow{3}{*}{$\sigma_A^*$} & 1                                & $0.111$                         & $0.061$ $(p=0.000)$          & $0.004$                             & $0.003 \pm 0.000$                             \\
                            &                               & 2                                & $0.285$                         & $0.185$ $(p=0.000)$          & $0.009$                             & $0.005 \pm 0.000$                             \\ 
                            &                               & 3                                & $1.150$                         & $0.850$ $(p=0.000)$          & $0.080$                             & $0.048 \pm 0.009$                             \\
                            & \multirow{3}{*}{$\phi_A^*$}   & 1                                & $0.830$                         & $-0.140$ $(p=0.000)$          & $0.048$                             & $0.016 \pm 0.003$                             \\
                            &                               & 2                                & $0.004$                         & $-0.826$ $(p=0.000)$          & $0.012$                             & $0.001 \pm 0.023$                             \\
                            &                               & 3                                & $0.000$                         & $-0.610$ $(p=0.000)$          & $0.000$                             & $0.000 \pm 0.000$                             \\ \hline

@@

        \noindent Table \arabic{tablenum}: Estimates and standard errors for the parameters of the distribution of acceleration across all four models in the simulation study. The ``Estimate" column is the average across 500 simulations, and the ``Observed Fisher SE" column is the median across 500 simulations. The $\pm$ refers to the inter-quartile range. SE stands for standard error. Note that standard error cannot be estimated when $\phi^*_A \approx 0$ or $\phi^*_A \approx 1$. Reported $p$-values test if the observed bias is statistically significant using a one-sample $t$-test.
        \addtocounter{tablenum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$ and $\hat \sigma^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$ and $\sigma^*_A$ for both subdive states. These estimates are for the HHMM-DFT. Note that the HHMM-DFT assumes no auto-correlation in $\Zone_{t,\tilde t^*}$, so $\hat \phi_A^{*(\cdot,i^*)}$ is absent from these plots.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHHMM. 
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of acceleration parameter estimates ($\hat \mu^*_A$, $\hat \sigma^*_A$, and $\hat \phi^*_A$) for each subdive state. The red star represents the true values of $\mu^*_A$, $\sigma^*_A$, and $\phi^*_A$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

                            &                               & 3                                & $9787.1$                         & $17.2$ $(p=0.718)$           & $1060.5$                            & $262.1 \pm 97.120$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.849$                         & $-0.001$ $(p=0.991)$         & $0.989$                             & $0.658 \pm 0.088$                             \\
                            &                               & 2                                & $514.21$                         & $-2.47$ $(p=0.010)$          & $21.43$                             & $9.74 \pm 0.81$                             \\
                            &                               & 3                                & $14430$                          & $-33$ $(p=0.647)$            & $1596$                              & $262 \pm 97$                             \\ \hline

@@

                            &                               & 3                                & $6841.0$                         & $-2929.0$ $(p=0.000)$        & $1164.3$                             & $198.2 \pm 77.1$                             \\
                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.800$                         & $-0.050$ $(p=0.351)$         & $1.192$                             & $0.679 \pm 0.100$                             \\
                            &                               & 2                                & $513.26$                         & $-3.42$ $(p=0.001)$          & $22.60$                             & $10.75 \pm 1.21$                             \\
                            &                               & 3                                & $11459$                          & $-3004$ $(p=0.000)$          & $1739$                              & $198 \pm 77$                             \\ \hline

@@

                            & \multirow{3}{*}{$\sigma_W^*$} & 1                                & $23.890$                         & $0.040$ $(p=0.401)$          & $1.058$                             & $0.661 \pm 0.093$                             \\
                            &                               & 2                                & $515.23$                         & $-1.45$ $(p=0.125)$          & $21.09$                             & $9.64 \pm 0.92$                             \\
                            &                               & 3                                & $14438$                          & $-25$ $(p=0.740)$            & $1661$                              & $280 \pm 136$                             \\

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the HHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \noindent Figure \arabic{fignum}: Kernel density estimate of the distributions of wiggliness parameter estimates ($\hat \mu^*_W$ and $\hat \sigma^*_W$) for each subdive state. The red star represents the true values of $\mu^*_W$ and $\sigma^*_W$ for both subdive states. These estimates are for the CarHMM-DFT.
        \addtocounter{fignum}{1}

@@

        \begin{center}
        \scalebox{0.75}{
        \bgroup
        \centering
        \def\arraystretch{1.5}
\begin{tabular}{ccccccc}
Model                        & \multicolumn{1}{c}{Parameter} & \multicolumn{1}{c}{Estimate}   & \multicolumn{1}{c}{Bias} & \multicolumn{1}{c}{Empirical SE} & \multicolumn{1}{c}{Observed Fischer SE}     \\ \hline
\multirow{2}{*}{CarHHMM-DFT}& $\Gamma_{12}$                 & $0.160$                         & $0.005$ $(p=0.030)$        & $0.056$                           & $0.042 \pm 0.012$                             \\
                             & $\Gamma_{21}$                 & $0.907$                         & $-0.006$ $(p=0.214)$        & $0.102$                           & $0.094 \pm 0.032$                             \\ \hline
\multirow{2}{*}{HHMM-DFT}   & $\Gamma_{12}$                 & $0.161$                         & $0.007$ $(p=0.007)$        & $0.055$                           & $0.041 \pm 0.011$                             \\
                             & $\Gamma_{21}$                 & $0.916$                         & $0.004$ $(p=0.372)$        & $0.088$                           & $0.091 \pm 0.028$                             \\ \hline
\multirow{2}{*}{CarHHMM}    & $\Gamma_{12}$                 & $0.198$                         & $0.044$ $(p=0.000)$        & $0.152$                           & $0.043 \pm 0.013$                             \\
                             & $\Gamma_{21}$                 & $0.832$                         & $-0.081$ $(p=0.000)$        & $0.195$                           & $0.093 \pm 0.034$                             \\ \hline
\multirow{2}{*}{CarHMM-DFT} & $\Gamma_{12}$                 & ------                         & ------                   & ------                           & ------                                      \\
                             & $\Gamma_{21}$                 & ------                         & ------                   & ------                           & ------                                      \\
\end{tabular}
        \egroup
        }
        \end{center}

        \noindent Table \arabic{tablenum}: Estimates and standard errors for coarse-scale probability transition matrices across all four models in the simulation study. The ``Estimate" column is the average across 500 simulations, and the ``Observed Fisher SE" column is the median across 500 simulations. The $\pm$ refers to the inter-quartile range. SE stands for standard error. Note that standard error cannot be estimated when $\Gamma_{i,j} \approx 0$. Reported $p$-values test if the observed bias is statistically significant using a one-sample $t$-test.
        \addtocounter{tablenum}{1}

@@

                             & $\Gamma^{*(1)}_{13}$          & $0.002$                         & $0.002$ $(p=0.000)$        & $0.004$                           & $0.009 \pm 0.004$                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.003$                         & $0.003$ $(p=0.000)$        & $0.008$                           & $0.014 \pm 0.005$                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.111$                         & $-0.001$ $(p=0.349)$        & $0.017$                           & $0.015 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.001$                         & $0.000$ $(p=0.000)$        & $0.002$                           & $0.003 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.151$                         & $0.001$ $(p=0.584)$        & $0.023$                           & $0.021 \pm 0.005$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.036$                         & $-0.000$ $(p=0.944)$        & $0.013$                           & $0.010 \pm 0.003$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.007$                         & $0.007$ $(p=0.000)$        & $0.024$                           & $0.025 \pm 0.015$                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.252$                         & $0.026$ $(p=0.000)$        & $0.096$                           & $0.063 \pm 0.028$                             \\ \hline

@@

                             & $\Gamma^{*(1)}_{13}$          & $0.003$                         & $0.003$ $(p=0.000)$        & $0.006$                           & $0.009 \pm 0.004$                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.005$                         & $0.005$ $(p=0.000)$        & $0.009$                           & $0.014 \pm 0.004$                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.109$                         & $-0.004$ $(p=0.000)$        & $0.018$                           & $0.016 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.002$                         & $0.002$ $(p=0.000)$        & $0.004$                           & $0.005 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.151$                         & $0.001$ $(p=0.712)$        & $0.031$                           & $0.023 \pm 0.006$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.037$                         & $0.002$ $(p=0.009)$        & $0.013$                           & $0.011 \pm 0.004$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.021$                         & $0.021$ $(p=0.000)$        & $0.026$                           & $0.023 \pm 0.012$                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.135$                         & $-0.091$ $(p=0.000)$        & $0.057$                           & $0.038 \pm 0.018$                             \\ \hline
\multirow{12}{*}{CarHHMM}    & $\Gamma^{*(1)}_{12}$          & $0.138$                         & $-0.114$ $(p=0.000)$        & $0.131$                           & $0.018 \pm 0.005$                             \\
                             & $\Gamma^{*(1)}_{13}$          & $0.023$                         & $0.022$ $(p=0.000)$        & $0.107$                           & $0.007 \pm 0.004$                             \\

@@

                             & $\Gamma^{*(1)}_{31}$          & $0.013$                         & $0.013$ $(p=0.000)$        & $0.022$                           & $0.011 \pm 0.005$                             \\

@@

                             & $\Gamma^{*(2)}_{12}$          & $0.056$                         & $-0.056$ $(p=0.000)$        & $0.035$                           & $0.008 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{13}$          & $0.002$                         & $0.002$ $(p=0.004)$        & $0.017$                           & $0.002 \pm 0.001$                             \\
                             & $\Gamma^{*(2)}_{21}$          & $0.069$                         & $-0.081$ $(p=0.000)$        & $0.032$                           & $0.011 \pm 0.003$                             \\
                             & $\Gamma^{*(2)}_{23}$          & $0.017$                         & $-0.019$ $(p=0.000)$        & $0.012$                           & $0.005 \pm 0.002$                             \\
                             & $\Gamma^{*(2)}_{31}$          & $0.011$                         & $0.011$ $(p=0.000)$        & $0.016$                           & $0.018 \pm 0.009$                             \\
                             & $\Gamma^{*(2)}_{32}$          & $0.138$                         & $-0.088$ $(p=0.000)$        & $0.079$                           & $0.037 \pm 0.016$                             \\ \hline
